### 2018-06-27 Sections/optimising_the_world.tex
Graph colouring etc

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{graph_colouring}
\caption{Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}.}\index{Graph colouring}\label{fig:graph_colouring}	
\end{figure}

@@

In this version of the map colouring problem, a valid colouring specifies a set of transmission frequencies that avoid interregional interference, and the chromatic number specifies the smallest possible radio spectrum that must be allocated to the stations\footnote{Spectrum is worth a lot of money!}.

>>>>

\begin{figure}[!htb]
\includegraphics[width=0.35\textwidth]{graph_colouring}
\caption{Example of a graph with 3-colouring, such that no two vertices connected by an edge share the same colour. For this particular graph, 3-colouring is optimal (in the sense that the number of colours in minimised). It can easily be seen upon inspection that no 2-colouring is possible for this graph. Thus, this graph's chromatic number is \mbox{$\chi(G)=3$}\index{Chromatic number}.}\index{Graph colouring}\label{fig:graph_colouring}	
\end{figure}

@@

In this version of the map colouring problem, a valid colouring specifies a set of transmission frequencies that avoid interregional interference, and the chromatic number specifies the smallest possible radio spectrum\index{Radio spectrum} that must be allocated to the stations\footnote{Spectrum is worth a lot of money!}.
